model_1

### 2020-11-29 model_1.Rmd
Added test models with 65+ and Pre-existing Condition variables

```{r variables, warning=FALSE, results='hide'}
df <- read.csv("covid-19.csv", header = TRUE)
df<-df%>%
  rename(case_rate_100k = 'Case.Rate.per.100000',
         death_rate_100k = 'Death.Rate.per.100000',
         population_density = 'Population.density.per.square.miles',
         white_pct = 'White...of.Cases',
         black_pct = 'Black...of.Cases',
         hispanic_pct = 'Hispanic...of.Cases',
         other_pct = 'Other...of.Cases',
         state_emergency = 'State.of.emergency',
         business_closed = 'Closed.other.non.essential.businesses',
         business_reopen = 'Began.to.reopen.businesses.statewide',
         mask_public='Mandate.face.mask.use.by.all.individuals.in.public.spaces',
         mask_legal='No.legal.enforcement.of.face.mask.mandate') %>%
  select(State, case_rate_100k, death_rate_100k,population_density, white_pct, black_pct, hispanic_pct, 
         other_pct, state_emergency, business_closed, business_reopen, mask_public, mask_legal, 
         Black...of.Total.Population, White...of.Total.Population,
         Percent.living.under.the.federal.poverty.line..2018., Percent.Unemployed..2018., X65.)
# Assign correct data types
cols.num <- c("white_pct","black_pct","hispanic_pct","other_pct")
df[cols.num] <- sapply(df[cols.num],as.numeric)
df$state_emergency=as.Date(df$state_emergency, format = "%m/%d/%Y")
df$business_closed=as.Date(df$business_closed, format = "%m/%d/%Y")
df$business_reopen=as.Date(df$business_reopen, format = "%m/%d/%Y")
head(df)
```

>>>>

```{r variables, warning=FALSE, results='hide'}
df <- read.csv("covid-19.csv", header = TRUE)
head(df)
df<-df%>%
  rename(case_rate_100k = 'Case.Rate.per.100000',
         death_rate_100k = 'Death.Rate.per.100000',
         population_18 = 'Population.2018',
         population_density = 'Population.density.per.square.miles',
         white_pct = 'White...of.Cases',
         black_pct = 'Black...of.Cases',
         hispanic_pct = 'Hispanic...of.Cases',
         other_pct = 'Other...of.Cases',
         state_emergency = 'State.of.emergency',
         business_closed = 'Closed.other.non.essential.businesses',
         business_reopen = 'Began.to.reopen.businesses.statewide',
         mask_public='Mandate.face.mask.use.by.all.individuals.in.public.spaces',
         mask_legal='No.legal.enforcement.of.face.mask.mandate',
         nonelderly_preexisting_condition = 'Nonelderly.Adults.Who.Have.A.Pre.Existing.Condition'
         ) %>%
  select(State, case_rate_100k, death_rate_100k, population_18, population_density, white_pct, black_pct, hispanic_pct, 
         other_pct, state_emergency, business_closed, business_reopen, mask_public, mask_legal, 
         Black...of.Total.Population, White...of.Total.Population,
         Percent.living.under.the.federal.poverty.line..2018., Percent.Unemployed..2018., X65., 
         nonelderly_preexisting_condition, Children.0.18
         )
# Assign correct data types
cols.num <- c("white_pct","black_pct","hispanic_pct","other_pct")
df[cols.num] <- sapply(df[cols.num],as.numeric)
df$state_emergency=as.Date(df$state_emergency, format = "%m/%d/%Y")
df$business_closed=as.Date(df$business_closed, format = "%m/%d/%Y")
df$business_reopen=as.Date(df$business_reopen, format = "%m/%d/%Y")
head(df)
```

```{r}
df <- df %>% 
  mutate(nonelderly_preexisting_condition_100k = nonelderly_preexisting_condition/(population_18*(1-X65.-Children.0.18)) * 100000,
         X65_100k = X65.*100000)
head(df)
```

```{r}
summary(df$nonelderly_preexisting_condition_100k)
```

```{r}
ggplot(data = df,
  mapping = aes(x= nonelderly_preexisting_condition_100k ))+
  geom_histogram(fill = 'skyblue', color = 'grey30') +
  labs(title =  "Histogram of Nonelderly Adults with Pre-Existing Conditions per 100,000", x = "Adults per 100,000", y = 'Count')
```

```{r}
ggplot(data = df,
  mapping = aes(x= X65_100k ))+
  geom_histogram(fill = 'skyblue', color = 'grey30', bins = 30) +
  labs(title =  "Histogram of Adults Over 65 per 100,000", x = "Adults over 65 per 100,000", y = 'Count')
```

```{r}
df %>% 
  ggplot(aes(nonelderly_preexisting_condition_100k, case_rate_100k)) + 
  geom_smooth(se = FALSE) +
  geom_point() +   
  labs(
    title = 'COVID Case Rate due to Nonelderly Adults with Pre-existing Conditions', 
    x = 'Nonelderly adults with pre-existing conditions per 100,000', 
    y = 'COVID case rate per 100,000'
  )
```

```{r}
df %>% 
  ggplot(aes(X65_100k, case_rate_100k)) + 
  geom_smooth(se = FALSE) +
  geom_point() +   
  labs(
    title = 'COVID Case Rate due to Adults Over 65', 
    x = 'Adults over 65 per 100,000', 
    y = 'COVID case rate per 100,000'
  )
```

```{r}
model_test <- lm(case_rate_100k ~ nonelderly_preexisting_condition_100k + X65_100k, data = df)
car::vif(model_test)
coeftest(model_test, vcov = vcovHC)
```

```{r}
model_test_65 <- lm(case_rate_100k ~ X65_100k, data = df)
coeftest(model_test_65, vcov = vcovHC)
```
